mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2023-01-16 rj/mathml.Rmd
amend
Update authors

```{r setup, include=FALSE}
# To do
#
# paste(x, y, z)
# Spacing
# Comma separated lists
# Ellipsis
# Radicals
# Subsets
# Greek letters in MathJax
# Typeface
# Stylechanges
# Phantoms

@@

# References

>>>>

```{r setup, include=FALSE}
# To do
#
# paste(x, y, z)--> z, y, z (Covered by quote ())

# Spacing: operator for separating elements in expression. E.g.,
## x ~ y --> x  y ;
## x ~ ~ y --> x    y

# Ellipsis: ldots or cdots. E.g., 
## x[1] + ... + x[n]

# Radicals sqrt(x, y) --> y√x

# Sets: some symbols in set relations are missing:
## supset, supseteq, notsubset, subset, subseteq, notin

# Phantom: command that produces a space in place of an argument (partially covered by omit() (?)). E.g.:
## x + phantom(0) + y --> x +    + y
## x + over(1, vphantom(0)) --> x + 1/

# Typeface: plain, bold, italic, bolditalic

# Stylechanges: textstyle(x), scriptstyle(x) scriptscript(x)

# linear models: DepVar ~ X0 + X1

# hat, overline, cancel, box, invisible, phantom

@@
